Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-24 fmics/paper.tex
tweaks

%To prove the equation above, we need to formalize all of its terms.
To make the above correctness statement more precise, we need to include the notion of time.
The count values arrive at the input of the SRS block every 40 micro-seconds, which we abstract as a single time step in our logical model.
We formalize the input stream as a function of time: $D\;t$ denotes the input value to the SRS structure at time $t$.
In addition, the terms in the above statement depend on this stream of input counts.
With these refinements, the correctness statement is: \[\forall{D\,n\,t} \cdot \,\mathsf{RS}\;D\;n\;t = \mathsf{exact}\;D\;\;n\;t\pm\text{acceptable error}\]

@@

%To formalize the term on the left hand side, we need to build a logical model of the SRS structure.
The first natural step to prove the correctness of the above statement is to build a logical model of the SRS structure.
Our work proceeded in two phases, starting with a model of a simplified structure and proceeding to a model which is closer to the SRS implementation in BLMS.
In both phases, we model each building block of the SRS structure that holds a count value--for example, each cell in each shift register--as a function in HOL that takes the input stream and current time step as inputs and returns the value the corresponding building block holds at that time.

@@

In the second phase, we eliminated the first four simplifications (listed above) by adding middle taps, a more flexible arrangement of slices, the subtractor and accumulator, and considering the delays that each block may introduce.
In both cases, however, the model is simultaneously a simplification and a generalization of the actual structure of SRS in BLMS in the following way: we model an infinite number of slices (rather than six slices), each with an infinite number of shift register cells and taps (rather than fixed width shift registers and only two taps), simply by letting indices range over the natural numbers without explicitly giving limits.
Such a parameterization would make the model and the analysis applicable to the future upgraded/modified versions of the system.

>>>>

%To prove the equation above, we need to formalize all of its terms.
To make the above correctness statement more precise, we need to include the notion of time.
The count values arrive at the input of the SRS block every 40 micro-seconds, which we abstract as a single time step in our logical model.
We formalize the input stream as a function of time: $D\;t$ denotes the input value to the SRS structure at time $t$.
In addition, the terms in the above statement depend on this stream of input counts.
With these refinements, the correctness statement becomes: \[\forall{D\,n\,t} \cdot \,\mathsf{RS}\;D\;n\;t = \mathsf{exact}\;D\;\;n\;t\pm\text{acceptable error}\]

@@

%To formalize the term on the left hand side, we need to build a logical model of the SRS structure.
The first natural step to prove the correctness statement is to build a logical model of the SRS structure.
Our work proceeded in two phases, starting with a model of a simplified structure and proceeding to a model which is closer to the SRS implementation in BLMS.
In both phases, we model each building block of the SRS structure that holds a count value -- for example, each cell in each shift register -- as a function in HOL that takes the input stream and current time step as inputs and returns the value the corresponding building block holds at that time.

@@

In the second phase, we eliminated the first four simplifications (listed above) by adding middle taps, a more flexible arrangement of slices, the subtractor and accumulator, and considering the delays that each block may introduce.
In both cases, however, the model is simultaneously a simplification and a generalization of the actual structure of SRS in BLMS in the following way: we model an infinite number of slices (rather than six slices), each with an infinite number of shift register cells and taps (rather than fixed width shift registers and only two taps), simply by letting indices range over the natural numbers without explicitly giving limits.
This parameterization makes the model and the analysis more likely to be applicable to future upgraded/modified versions of the system.
